Compositional Certified Resource Bounds

### 2014-07-03 paper/main.tex
typo
bounds in comparison table

\subsection{Implementation}

We implemented the new automatic amortized analysis using CIL [XXX].
CIL is a subset of C that is very similar to CompCert Clight but
provides tool support that facilitated the implementation.  The
implementation is publically available at XXX.  More details can be
found in section XXX.

We do not yet generate certificates in the program logic that are
checkable in Coq.  This is substantial additional engineering effort
but is conceptually straightforward as we describe in detail in
Section XXX.

@@

\begin{figure*}
\centering
\begin{tabular}{t|c|c|c|c}
%
&
\begin{lstlisting}
while (y > x) {
  x++; tick(1) }
while (x > 2) {
  x -= 3; tick(1) }
\end{lstlisting}
&
\begin{lstlisting}
while (i > 100)
  i--;
i += k+50;
while (i >= 0)
  i--;
\end{lstlisting}
&
\begin{lstlisting}
while (x > 0) {
  x--;
  t=x, x=y, y=t;
}
\end{lstlisting}
&
\begin{lstlisting}
assert(y >= 0);
while (x>y) {
  x -= y+1;
  for (z=y; z > 0; z--)
    /* skip */;
}
\end{lstlisting}
\\
%
\hline
& t08a (slightly modified t08) & t19 & t30 & t15
%
\\
\hline
LOOPUS \\
Rank \\
AAA
\end{tabular}
\caption{ Comparison of resource bounds derived by different tools on
  several examples with linear bounds.  AAA stands for our automatic
  amortized analysis for Clight.  The output of Rank has been manually
  simplified to fit the table.  }
\label{fig:compar}
\end{figure*}

>>>>

@@

\begin{figure*}
\centering
\begin{tabular}{r|c|c|c|c}
%
&
\begin{lstlisting}
while (y > x) {
  x++; tick(1); }
while (x > 2) {
  x -= 3; tick(1); }
\end{lstlisting}
&
\begin{lstlisting}
while (i > 100) {
  i--; tick(1) }
i += k+50;
while (i >= 0) {
  i--; tick(1); }
\end{lstlisting}
&
\begin{lstlisting}
while (x > 0) {
  x--;
  t=x, x=y, y=t;
  tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}
assert(y >= 0);
while (x>y) {
  x -= y+1;
  for (z=y; z > 0; z--)
    tick(1);
  tick(1);
}
\end{lstlisting}
\\
%
\hline
& t08a (slightly modified t08) & t19 & t30 & t15
%
\\
\hline
LOOPUS &
{\small XXX} &
{\small $\max(0, \! i{-}10^2) \!+ \max(0, \! k {+} i {+} 51)$} &
{\small % $1 + \max(x, y)$ (???)
---
} &
---
\\
%
%
%
%
Rank &
{\small $2 {+} y {-} x (???)$ } &
{\small $54+k+i$ } &
--- &
{\small $2+2x-y$ }
\\
%
%
AAA 
  & {\small $1.33|[x,y]| {+} 0.33 |[0,x]|$ }
  & $50 {+} |\inter {-1} i| {+} |\inter 0 k|$ 
  & $|\inter 0 x| {+} |\inter 0 y|$
  & $|\inter 0 x|$
\end{tabular}
\caption{ Comparison of resource bounds derived by different tools on
  several examples with linear bounds.  AAA stands for our automatic
  amortized analysis for Clight.  The output of Rank has been manually
  simplified to fit the table.  }
\label{fig:compar}
\end{figure*}
